---
title: "First Employment and Job Relevance"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    self_contained: TRUE
    theme: lumen
    css: ILOVEBULSU.css
---

```{r setup, include = F}

knitr::opts_chunk$set(warning    = F,
                      message    = F,
                      echo       = F)

library(flexdashboard)
library(tidyverse)
library(plotly)
library(DT)
library(survival)
library(broom)

source("Analysis.R")



# ---- Formats ----

## Pie charts

pie_plotly <- function(df, category_col) {
  original <- levels(df[[category_col]])
  if (is.null(original)) original <- unique(df[[category_col]])
  
  df[[category_col]] <- factor(df[[category_col]],
                               levels = df[[category_col]][order(df$count,
                                                                 decreasing = T)])
  
  plot_ly(
    data         = df,
    labels       = ~.data[[category_col]],
    values       = ~count,
    type         = "pie",
    text         = ~paste0(count, "<br>",
                           round(count / sum(count) * 100, 0),
                           "%"),
    textinfo     = "text",
    textposition = "outside",
    marker       = list(colors = c("#4682B4",
                                   "#FF7F50",
                                   "#2E8B57",
                                   "#B22222",
                                   "#9370DB",
                                   "#7F7F7F")),
    hoverinfo    = "text",
    hovertext    = ~paste(.data[[category_col]], "<br>Count:", count)) |>
    layout(showlegend = T,
           legend = list(orientation = "v",
                         x           = 1.05,
                         y           = 0.5,
                         xanchor     = "left",
                         yanchor     = "middle"))
}



# ---- Coefficients ----

## Cox

coxBestAlt$estimate

cox_Age    <- -0.25
cox_Sex_F  <- -0.26
cox_BSES   <-  0.34
cox_BSFT   <-  0.68
cox_BSM_AS <-  0.25
cox_BSM_BA <-  0.47
cox_BSM_CS <-  0.09
cox_Year   <- -0.18
cox_Exams  <- -0.20

## AFT

aftBestAlt$estimate

aft_Inter  <-  1.86
aft_Age    <-  0.35
aft_Sex_F  <-  0.35
aft_BSES   <- -0.48
aft_BSFT   <- -0.90
aft_BSM_AS <- -0.33
aft_BSM_BA <- -0.68
aft_BSM_CS <- -0.12
aft_Year   <-  0.21
aft_Exams  <-  0.27
aft_Log    <-  0.30

# RPS

rpsBestAlt$term

rps_Inter  <- -3.10
rps_Age    <- -0.26
rps_Sex_F  <- -0.26
rps_BSES   <-  0.36
rps_BSFT   <-  0.67
rps_BSM_AS <-  0.24
rps_BSM_BA <-  0.50
rps_BSM_CS <-  0.09
rps_Year   <- -0.16
rps_Exams  <- -0.20
rps_Log    <-  6.68

```


# Distribution of Graduates Across Demographic Profiles

Row {.tabset .tabset-fade}
-------------------------------------

### Age

```{r}

age <- ggplot(tibbleList$Age,
              aes(x    = Age,
                  y    = count,
                  text = paste0(round(count / sum(count) * 100, 0),
                                "%"))) +
  geom_col(fill  = "#4682B4",
           width = 1) +
  theme_minimal()

ggplotly(age)

```

### Sex

```{r}

pie_plotly(tibbleList$Sex, "Sex")

```



# Distribution of Graduates Across Academic Profiles

Row {.tabset .tabset-fade}
-------------------------------------

### Undergraduate Program
    
```{r}

ugp <- ggplot(tibbleList$`Undergraduate program`,
              aes(x    = `Undergraduate program`,
                  y    = count,
                  text = paste0(round(count / sum(count) * 100, 0),
                                "%"))) +
  geom_col(fill = "#4682B4") +
  coord_flip() +
  theme_minimal()

ggplotly(ugp)

```

### Program Preference

```{r}

pie_plotly(tibbleList$`Program preference`, "Program preference")

```

### Graduation Year

```{r}

gy <- ggplot(tibbleList$`Graduation year`,
              aes(x    = `Graduation year`,
                  y    = count,
                  text = paste0(round(count / sum(count) * 100, 0), "%"))) +
  geom_col(fill  = "#4682B4",
           width = 1) +
  theme_minimal()

ggplotly(gy)

```

### Postgraduate Education

```{r}

pie_plotly(tibbleList$`Postgraduate education`, "Postgraduate education")

```

### Professional Exams

```{r}

pfe <- ggplot(tibbleList$`Professional exams`,
              aes(x    = `Professional exams`,
                  y    = count,
                  text = paste0(round(count / sum(count) * 100, 0), "%"))) +
  geom_col(fill  = "#4682B4",
           width = 1) +
  theme_minimal()

ggplotly(pfe)

```



# Distribution of Graduates Across Professional Profiles

Row {.tabset .tabset-fade}
-------------------------------------

### Employment Status

```{r}

pie_plotly(tibbleList$`Status string`, "Status string")

```

### Nature of Employment

```{r}

pie_plotly(tibbleList$`Nature of employment`, "Nature of employment")

```

### Employment Qualification

```{r}

pie_plotly(tibbleList$`Employment qualification`, "Employment qualification")

```

### Employment Wait time

```{r}

ewt <- ggplot(survey, aes(x = `Employment wait time`)) + 
  geom_histogram(binwidth = 5,
                 fill     = "#4682B4") +
  theme_minimal()

ggplotly(ewt)

```

### Sector of Employment

```{r}

soe <- ggplot(tibbleList$`Sector of employment`,
              aes(x    = reorder(`Sector of employment`, -count),
                  y    = count,
                  text = paste0(round(count / sum(count) * 100, 0), "%"))) +
  geom_col(fill  = "#4682B4",
           width = 1) +
  theme_minimal()

ggplotly(soe)

```



# Kaplan--Meier Estimation

Row {.tabset .tabset-fade}
-------------------------------------

### Kaplan–Meier Curves Across Different Categorical Variables

```{r}

# ---- Variables ----

names(survey) <- make.names(names(survey))

kmVars <- c("Sex", "Undergraduate.program", "Postgraduate.education") 

kmVars_full <- c("All", kmVars)

# ---- Plotly ----

curvs <- plot_ly()

trace_map <- list()
trace_count <- 0

# ---- Generate curvs ----

for (strat in kmVars_full) {
  
  if (strat == "All") {
    
    kmFit <- survfit(Surv(Employment.wait.time,
                          Status) ~ 1,
                     data = survey)
    
    df <- broom::tidy(kmFit)
    df$strata <- "All"
    
    } else {
      
      kmFit <- survfit(reformulate(strat,
                                   response = "Surv(Employment.wait.time, Status)"),
                       data = survey)
      
      df <- broom::tidy(kmFit)
      
      if (is.null(df$strata)) {
        
        df$strata <- strat
        
        }
      }
  
  strata_levels <- unique(df$strata)
  trace_map[[strat]] <- c()
  
  for (s in strata_levels) {
    
    trace_count <- trace_count + 1
    
    df_sub <- df |>
      filter(strata == s)
    
    curvs <- curvs |>
      add_lines(data    = df_sub,
                x       = ~time,
                y       = ~estimate,
                name    = s,
                visible = (strat == kmVars_full[1]),
                line    = list(shape = "hv"))
    
    trace_map[[strat]] <- c(trace_map[[strat]], trace_count)
    
    }
  }

# ---- Dropdown ----

buttons <- list()

for (i in seq_along(kmVars_full)) {
  
  strat <- kmVars_full[i]
  
  vis <- rep(F, trace_count)
  vis[trace_map[[strat]]] <- T
  
  buttons[[i]] <- list(method = "update",
                       args   = list(list(visible = vis)),
                       label  = gsub("\\.", " ", strat))
  
  }

# ---- Plots ----

curvs <- curvs |>
  layout(title       = "Kaplan-Meier Survival Curves",
         xaxis       = list(title = "Employment Wait Time (Weeks)"),
         yaxis       = list(title = "Probability of Unemployment"),
         updatemenus = list(list(type    = "dropdown",
                                 buttons = buttons,
                                 x       = 0.1,
                                 y       = 1.15)))

curvs

```

### Summary Statistics Based on Kaplan–Meier Estimation

```{r}

datatable(kmSummaryAlt,
          rownames = F,
          options  = list(pageLength = 10,
                          dom        = 'tip',
                          ordering   = T,
                          paging     = F),
          class    = 'compact stripe')

```



# Cox Proportional Hazards Regression

Row {.tabset .tabset-fade}
-------------------------------------
    
### Cox Regression Model
    
```{r}

datatable(coxBestAlt,
          rownames = F,
          options  = list(pageLength = 9,
                          dom        = 'tip',
                          ordering   = T,
                          paging     = F),
          class    = 'compact stripe')

```

### Estimations

```{r}

# ---- Entries ----

examples <- list("Baseline" = c(Age    = 0,
                                Sex_F  = 0,
                                BSES   = 0,
                                BSFT   = 0,
                                BSM_AS = 0,
                                BSM_BA = 0,
                                BSM_CS = 0,
                                Year   = 0,
                                Exams  = 0),
                 
                 "Example 1" = c(Age    = 1,
                                 Sex_F  = 1,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 0,
                                 BSM_BA = 1,
                                 BSM_CS = 0,
                                 Year   = 2,
                                 Exams  = 1),
                 
                 "Example 2" = c(Age    = -1,
                                 Sex_F  = 0,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 1,
                                 BSM_BA = 0,
                                 BSM_CS = 0,
                                 Year   = 4,
                                 Exams  = 1),
                 
                 "Example 3" = c(Age    = 0,
                                 Sex_F  = 1,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 0,
                                 BSM_BA = 0,
                                 BSM_CS = 0,
                                 Year   = 0,
                                 Exams  = 0),
                 
                 "Example 4" = c(Age    = 1,
                                 Sex_F  = 0,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 1,
                                 BSM_BA = 0,
                                 BSM_CS = 0,
                                 Year   = 0,
                                 Exams  = 1),
                 
                 "Example 5" = c(Age    = 1,
                                 Sex_F  = 0,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 0,
                                 BSM_BA = 0,
                                 BSM_CS = 1,
                                 Year   = 0,
                                 Exams  = 1))

# ---- Coefficientss ----

coeffs <- c(Age    = cox_Age,
            Sex_F  = cox_Sex_F,
            BSES   = cox_BSES,
            BSFT   = cox_BSFT,
            BSM_AS = cox_BSM_AS,
            BSM_BA = cox_BSM_BA,
            BSM_CS = cox_BSM_CS,
            Year   = cox_Year,
            Exams  = cox_Exams)

baseline <- examples[["Baseline"]]

# ---- Computation ----

hazrat <- function(x) {
  
  nz <- x[x != 0]
  delta <- x - baseline
  
  terms <- sapply(names(x),
                  function(nm) {
                    
                    val  <- x[nm]
                    dval <- delta[nm]
                    
                    color <- ifelse(dval == 0, "#000000", "#FF0000")
                    
                    paste0("<span style='color:", color, "'>", nm, "(", val, ")</span>")
  
                    })
  
  lp <- sum(coeffs * x)
  hr <- exp(lp)
  
  list(formula = paste0("h(t) = ",
                        paste(terms,
                              collapse = " + ")),
       hr      = hr,
       delta   = delta)
  
  }

# ---- Plotly ----

estims <- plot_ly()

for (i in seq_along(examples)) {
  
  name <- names(examples)[i]
  x    <- examples[[i]]
  
  res  <- hazrat(x)
  
  estims  <- estims |>
    add_trace(x          = 0,
              y          = 0,
              type       = "scatter",
              mode       = "text",
              text       = paste0("<b>", name,
                                  "</b><br><br>", res$formula, "<br><br>",
                                  "Hazard Ratio ≈ ", round(res$hr, 2),
                                  ", ", (1 - round(res$hr, 2)) * 100,
                                  "% slower than the baseline"),
              textfont   = list(family = "Arial", size = 16),
              visible    = (i == 1),
              showlegend = F)
  
  }

# ---- Dropdown ----

buttons <- lapply(seq_along(examples), function(i) {
  
  vis <- rep(F,
             length(examples))
  
  vis[i] <- T
  list(method = "update",
       args   = list(list(visible = vis)),
       label  = names(examples)[i])
  
  })

# ---- Estimates ----

estims <- estims |>
  layout(title       = "Cox Regression Hazard Ratio Estimation",
         xaxis       = list(visible = F),
         yaxis       = list(visible = F),
         updatemenus = list(list(type = "dropdown",
                                 buttons = buttons,
                                 x = 0.1,
                                 y = 1.2)),
         dragmode = F) |>
  config(displayModeBar = F)

estims

```



# Accelerated Failure Time Modeling

Row {.tabset .tabset-fade}
-------------------------------------
    
### AFT Model
    
```{r}

datatable(aftBestAlt,
          rownames = F,
          options  = list(pageLength = 11,
                          dom        = 'tip',
                          ordering   = T,
                          paging     = F),
          class    = 'compact stripe')

```

### Estimations

```{r}

# ---- Entries ----

examples <- list("Baseline" = c(Age    = 0,
                                Sex_F  = 0,
                                BSES   = 0,
                                BSFT   = 0,
                                BSM_AS = 0,
                                BSM_BA = 0,
                                BSM_CS = 0,
                                Year   = 0,
                                Exams  = 0),
                 
                 "Example 1" = c(Age    = 1,
                                 Sex_F  = 1,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 0,
                                 BSM_BA = 1,
                                 BSM_CS = 0,
                                 Year   = 2,
                                 Exams  = 1),
                 
                 "Example 2" = c(Age    = -1,
                                 Sex_F  = 0,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 1,
                                 BSM_BA = 0,
                                 BSM_CS = 0,
                                 Year   = 4,
                                 Exams  = 1),
                 
                 "Example 3" = c(Age    = 0,
                                 Sex_F  = 1,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 0,
                                 BSM_BA = 0,
                                 BSM_CS = 0,
                                 Year   = 0,
                                 Exams  = 0),
                 
                 "Example 4" = c(Age    = 1,
                                 Sex_F  = 0,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 1,
                                 BSM_BA = 0,
                                 BSM_CS = 0,
                                 Year   = 0,
                                 Exams  = 1),
                 
                 "Example 5" = c(Age    = 1,
                                 Sex_F  = 0,
                                 BSES   = 0,
                                 BSFT   = 0,
                                 BSM_AS = 0,
                                 BSM_BA = 0,
                                 BSM_CS = 1,
                                 Year   = 0,
                                 Exams  = 1))

# ---- Coefficientss ----

coeffs <- c(Age    = aft_Age,
            Sex_F  = aft_Sex_F,
            BSES   = aft_BSES,
            BSFT   = aft_BSFT,
            BSM_AS = aft_BSM_AS,
            BSM_BA = aft_BSM_BA,
            BSM_CS = aft_BSM_CS,
            Year   = aft_Year,
            Exams  = aft_Exams)

baseline <- examples[["Baseline"]]

# ---- Computation ----

hazrat <- function(x) {
  
  nz <- x[x != 0]
  delta <- x - baseline
  
  terms <- sapply(names(x),
                  function(nm) {
                    
                    val  <- x[nm]
                    dval <- delta[nm]
                    
                    color <- ifelse(dval == 0, "#000000", "#FF0000")
                    
                    paste0("<span style='color:", color, "'>", nm, "(", val, ")</span>")
  
                    })
  
  lp <- aft_Inter + sum(coeffs * x)
  tr <- exp(lp)
  
  list(formula = paste0("log(t) = ",
                        "Intercept + ",
                        paste(terms,
                              collapse = " + ")),
       tr      = tr,
       delta   = delta)
  
  }

# ---- Plotly ----

estims <- plot_ly()

for (i in seq_along(examples)) {
  
  name <- names(examples)[i]
  x    <- examples[[i]]
  
  res  <- hazrat(x)
  
  estims  <- estims |>
    add_trace(x          = 0,
              y          = 0,
              type       = "scatter",
              mode       = "text",
              text       = paste0("<b>", name,
                                  "</b><br><br>", res$formula, "<br><br>",
                                  "Time Ratio ≈ ", round(res$tr, 2),
                                  " weeks, ", (round(res$tr, 2) - 6.42),
                                  " week longer than the baseline"),
              textfont   = list(family = "Arial", size = 16),
              visible    = (i == 1),
              showlegend = F)
  
  }

# ---- Dropdown ----

buttons <- lapply(seq_along(examples), function(i) {
  
  vis <- rep(F,
             length(examples))
  
  vis[i] <- T
  list(method = "update",
       args   = list(list(visible = vis)),
       label  = names(examples)[i])
  
  })

# ---- Estimates ----

estims <- estims |>
  layout(title       = "AFT Time Ratio Estimation",
         xaxis       = list(visible = F),
         yaxis       = list(visible = F),
         updatemenus = list(list(type = "dropdown",
                                 buttons = buttons,
                                 x = 0.1,
                                 y = 1.2)),
         dragmode = F) |>
  config(displayModeBar = F)

estims

```



# Royston--Parmar Splines

Row {.tabset .tabset-fade}
-------------------------------------
    
###  RPS Model
    
```{r}

datatable(rpsBestAlt,
          rownames = F,
          options  = list(pageLength = 11,
                          dom        = 'tip',
                          ordering   = T,
                          paging     = F),
          class    = 'compact stripe')

```

### Estimations

```{r}



```



<!-- # Comparison Between Three Survival Models by Fit Indices -->

<!-- ```{r} -->

<!-- datatable(bestAlt, -->
<!--           rownames = F, -->
<!--           options  = list(pageLength = 10, -->
<!--                           dom        = 'tip', -->
<!--                           ordering   = T, -->
<!--                           paging     = F), -->
<!--           class    = 'compact stripe') -->


<!-- ``` -->



<!-- # Performance Metrics of the Three Fitted Data Mining Models -->

<!-- ```{r} -->

<!-- convert_latex_to_html <- function(x) { -->
<!--   gsub("\\\\textcolor\\{([^}]*)\\}\\{([^}]*)\\}", -->
<!--        "<span style='color:\\1;'>\\2</span>", -->
<!--        x, -->
<!--        perl = T) -->
<!-- } -->

<!-- allCMAlt[] <- lapply(allCMAlt, -->
<!--                      function(col) { -->
<!--   if (is.character(col)) { -->
<!--     convert_latex_to_html(col) -->
<!--   } else { -->
<!--     col -->
<!--   } -->
<!-- }) -->

<!-- datatable(allCMAlt, -->
<!--           rownames = F, -->
<!--           escape   = F, -->
<!--           options  = list(pageLength = 10, -->
<!--                           dom        = 'tip', -->
<!--                           ordering   = T, -->
<!--                           paging     = F), -->
<!--           class    = 'compact stripe') -->

<!-- ``` -->



<!-- # Raw Dataset -->

<!-- ```{r} -->

<!-- datatable(survey, -->
<!--           options  = list(pageLength = 5), -->
<!--           rownames = F) -->

<!-- ``` -->